---
output:
  html_document:
    highlight: tango
    theme: readable
css: ../css/customh5.css
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr); library(dplyr); library(reshape2)
library(knitr); library(kableExtra)


lec <- data.frame(filenames = paste0('lecture/', list.files("lecture", pattern='*.pdf|*.html')))
read <- data.frame(filenames = paste0('reading/', list.files("reading", pattern='*.pdf|*.html')))
hw <- data.frame(filenames = paste0('hw/', list.files("hw", pattern='*.pdf|*.html')))

out.lec <- lec %>% mutate(name = gsub("lecture/",  "", filenames), 
                          type = str_extract(lec$filenames,"\\.[a-z]{3}"),
                          nam = gsub(".html|.pdf", "", name), 
                          link = sprintf("[%s](%s)",type, filenames))

out.read <- read %>% mutate(name = gsub("reading/",  "", filenames), 
                            link = sprintf("[%s](%s)",name, filenames))

out.hw <- hw %>% mutate(name = gsub("hw/",  "", filenames), 
                          type = str_extract(hw$filenames,"\\.[a-z]{3}"),
                          nam = gsub(".html|.pdf", "", name), 
                          link = sprintf("[%s](%s)",type, filenames))
```

## Lecture Notes
The [Applied Statistics Notebook](https://norcalbiostat.github.io/AppliedStatistics_notes/index.html) (Abbreviated as **AS Notebook**) is a general set of notes that span multiple topics from 315, 615 and 456.  

```{r, message=FALSE, warning=FALSE, echo=FALSE}
x = out.lec %>% select(link, type, nam) %>% dcast(nam~type, value.var="link") %>% 
    kable(format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```

## Reading Materials
```{r, message=FALSE, warning=FALSE, echo=FALSE}
x = out.read %>% select(link) %>% kable(format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive" ,"bordered"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```

## Videos

### Passion Driven Stats

* Chapter 01 Course Introduction http://passiondrivenstatistics.com/2015/05/20/chapter-01-course-introduction/
* Chapter 02 http://passiondrivenstatistics.com/2015/06/02/chapter-2-draft-version/
* Chapter 04 http://passiondrivenstatistics.com/2015/09/16/chapter-04/ 
* Chapter 06 http://passiondrivenstatistics.com/2015/12/18/r-chapter-6/
* Chapter 07 http://passiondrivenstatistics.com/2016/01/08/r-chapter-7/
* Chapter 08 http://passiondrivenstatistics.com/2016/01/20/r-chapter-8/
* Chapter 09 http://passiondrivenstatistics.com/2016/03/28/r-chapter-9/
* Chapter 10 Probability http://passiondrivenstatistics.com/2015/07/15/chapter-10/ 
* Chapter 11 http://passiondrivenstatistics.com/2016/05/11/r-chapter-11/
* Chapter 12 http://passiondrivenstatistics.com/2016/06/29/r-chapter-12/
* Chapter 14 http://passiondrivenstatistics.com/2016/08/20/r-chapter-14/
* Chapter 17 http://passiondrivenstatistics.com/2016/10/06/r-chapter-17/
* Chapter 18 Writing for your poster http://passiondrivenstatistics.com/2018/06/08/chapter-18-writing-for-your-poster-presentation/




## Homework
Always **right click** and **save as** when saving RMD templates to your computer. 

* Homework 01 template [[RMD]](hw/hw01_template.Rmd)
```{r, message=FALSE, warning=FALSE, echo=FALSE}
x = out.hw %>% select(link, type, nam) %>% dcast(nam~type, value.var="link") %>% 
    kable(format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive" ,"bordered"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```



