---
output:
  html_document:
    toc: yes
    toc_float: yes
---

<br>

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr); library(dplyr); library(reshape2)
library(knitr); library(kableExtra)
options(knitr.kable.NA = '')

lec <- data.frame(filenames = paste0('lecture/', list.files("lecture", pattern='*.pdf|*.html')))
read <- data.frame(filenames = paste0('reading/', list.files("reading", pattern='*.pdf|*.html')))
hw <- data.frame(filenames = paste0('hw/', list.files("hw", pattern='template|*.pdf|*.html')))

out.lec <- lec %>% mutate(name = gsub("lecture/",  "", filenames), 
                          type = str_extract(lec$filenames,"\\.[a-z]{3}"),
                          type = ifelse(type=="tml", "html", type),
                          nam = gsub(".html|.pdf", "", name), 
                          link = sprintf("[%s](%s)",type, filenames))

out.read <- read %>% mutate(name = gsub("reading/",  "", filenames), 
                            name = gsub(".pdf", "", name),
                            link = sprintf("[%s](%s)",name, filenames))

out.hw <- hw %>% mutate(name = gsub("hw/",  "", filenames), 
                          type = str_extract(hw$filenames,".{3}$"),
                          type = ifelse(type=="tml", "html", type),
                          nam = gsub(".html|.pdf|.Rmd", "", name), 
                          link = sprintf("[%s](%s)",type, filenames))
```


# PDS Videos

* Video 01 Introduction to Passion Driven Statistics (5:49) https://youtu.be/_8A0zx51BKs
* Video 02 Data Sets and Code Books (24:37) https://passiondrivenstatistics.com/2015/06/02/chapter-2-draft-version/
* Video 03 Literature Review (7:57) https://passiondrivenstatistics.com/2015/09/16/chapter-04/
* Video 04 Working with Data (33:34) https://passiondrivenstatistics.com/2015/12/18/04r/
* Video 05 Data Management (33:28) https://passiondrivenstatistics.com/2016/01/08/r-chapter-7/
* Video 06 Graphing: One Variable at a Time (31:33) https://passiondrivenstatistics.com/2016/01/20/r-chapter-8/
* Video 07 Graphing Relationships (36:11) https://passiondrivenstatistics.com/2016/03/28/r-chapter-9/
* Video 08 Hypothesis Testing (30:46) https://passiondrivenstatistics.com/2015/07/15/chapter-10/
* Video 09 ANOVA (29:48) https://passiondrivenstatistics.com/2016/05/11/r-chapter-11/
* Video 10 Chi-Square Test of Independence (28:36) https://passiondrivenstatistics.com/2016/06/29/r-chapter-12/
* Video 11 Correlation (13:43) https://passiondrivenstatistics.com/2019/01/08/11-correlation/  
* Video 12 Moderating (21:29) https://passiondrivenstatistics.com/2016/08/20/r-chapter-14/
* Video 13 The Question of Causation (14:06) https://passiondrivenstatistics.com/2018/11/13/13-the-question-of-causation/
* Video 14 Multivariable Models and Confounding (57:43) https://passiondrivenstatistics.com/2016/10/06/r-chapter-17/ 
* Video 15 Writing for your poster (16:03) https://passiondrivenstatistics.com/2018/06/08/chapter-18-writing-for-your-poster-presentation/

# Donatello's Videos

* Welcome to Spring 19 https://670832.kaf.kaltura.com/media/Welcome+intro+video+sp19/0_non0k1h7
* Importing Data into R https://670832.kaf.kaltura.com/media/How+to+import+data+into+R/0_w6buqbaw

----

# Homework 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
x = out.hw %>% select(link, type, nam) %>% dcast(nam~type, value.var="link") %>% 
    kable(format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive" ,"bordered"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```

----

# Additional Lecture Notes
```{r, message=FALSE, warning=FALSE, echo=FALSE}
x = out.lec %>% select(link, type, nam) %>% dcast(nam~type, value.var="link") %>% 
    kable(format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", "bordered"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```

Also available is the [Applied Statistics Notebook](https://norcalbiostat.github.io/AppliedStatistics_notes/index.html) (Abbreviated as **AS Notebook**) is a general set of notes that span multiple topics from 315, 615 and 456.  


# Articles
```{r, message=FALSE, warning=FALSE, echo=FALSE}
x = out.read %>% select(link) %>% kable(format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive" ,"bordered"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```


