---
title: 'Project Information'
date: "Last Updated `r Sys.time()`"
output:
  html_document:
    highlight: tango
    theme: readable
    toc: yes
    toc_float: yes
css: css/customh5.css
---

Throughout the entire semester you will be analyzing a data set with the end goal of creating a poster presentation to present your research. Often your homework serves as a first draft of exploration into your research questions, and helps you build your story. Homework assignments alone will not be sufficient for a good analysis. 

# Peer Review

Project based assignments are subject to peer review. 

## Purpose

Why do we do peer review instead of just getting feedback from you? 

* Everyone has different thought processes and may have approached the question from a different perspective that can help you learn the material. 
* Co-authoring and reviewing your peers work is part of a professional research position. 
* Learning how to provide good feedback will make you a better collaborator
* This is a delayed version of paired programming - another set of eyeballs can typically help you find your mistake. 
* I have 10fold more assignments to review than you do. You'll get your peer's reviews back faster than I can get yours back.
* I will be looking for different things than your peers will be. This is a good thing. They are looking from "untrained eyes", which can be very critical to make sure you are explaining yourself clearly. I can better "figure out" what you are meaning to say  - they are the ones that will best tell you when/where you need to explain your findings better. 
* You have the _option_ to then take your peer's feedback and revise your homework before you turn it in for grading. 


## Process

How do I conduct a Peer Review

1. Check the [Peer Review Rotation](https://docs.google.com/spreadsheets/d/15BXa0Xx-utXAFUE5wlZDD-Z6ywV2ffLMiY4TThSnDJM/edit?usp=sharing) spreadsheet to see who you are scheduled to review. 
2. Open the assignment file in Google Drive directly. 
3. Change from "editing" to "suggesting" in the top right. 
    - If the assignment was uploaded as a PDF then use the comment tool in the top right to leave your comments. 
4. By editing the veribiage directly, or using comment bubbles, provide feedback to your peers. 
    - Be specific. Give the type of feedback that you want to recieve. 
    - Minimum four positive comments about what they did well, or should continue to do.
    - Minimum four corrections or suggestions for improvement. If it is reworking/grammer make these edits directly in the document. Explain why what you found was wrong and show how to do it correctly. 

**Revision period**

After you receive your peer feedback you have the _option_ of revising your work before I grade it. Turn in the final version in Blackboard learn 
    
## Feedback 

How to give good feedback

* Compliment the author. What did you like about their writing? 
* Make specific suggestions regarding things like word choices, use of details, organization, topic
* Mark corrections such as spelling, grammer, punctuation, analysis methods, coding errors
* Don't try to turn their paper or style into your style. 
* If you find a claim that is not supported by data in the document (or cited) be sure to point it out. 

Other resources (i'm always looking for more)

* https://blog.scholasticahq.com/post/how-to-write-helpful-peer-review-comments/
* Look at the questions posed in the bubbles for each section. https://violentmetaphors.com/2013/12/13/how-to-become-good-at-peer-review-a-guide-for-young-scientists/ 
* https://blog.cengage.com/top_blog/suggested-guidelines-for-student-peer-review/


## Grading of peer reviews

As I do my reviews on the same document, I will be reading and assessing your peer review. If I find your review is not providing quality feedback to the author you will not recieve credit for that review. You may see the cells in the peer review spreadsheet changing color as I check off your review. 


# Poster preparation

You will organize your research in stages by building a "powerpoint" type presentation. This will help you concicely explain your research topic and findings in a way that you can more easily translate (fit) onto a poster. 

## <span style="color:blue">**Setup / Overview**</span>
* Create a Google Slides presentation directly into the Project Slides folder in our Google Drive. 
* Name your file using your analysis pair names: `last_last` only. 
* The required contents for each slide are listed below under **Stages**
* At each stage you should update anything you need to change, such as correctly making graphics, writing results correctly etc. 
* This includes reviewing the current set of feedback and mak the appropriate corrections. 
    - Once you have addressed a particular piece of feedback mark it as "resolved" in Google Slides. 
* Your presentation should be limited to approximately 16-18 slides. The contents of each slide are listed below. 


## <span style="color:blue">**Stage 1**</span>
1. Title 
2. Introduction 
3. Background & lit review. 
4. Explain the research problem
5. State your Research Question. 
6. Introduce the data. Where does it come from, how was it collected. How many records? 
7. Description of measures (variables) being used. Explain any recoding and/or altering that was done. 
    - This refers to significant changes to the data (making new variables, dichotomizing or categorizing existing variables)
    - Do NOT discuss setting missing codes such as 98 and 99 to `NA`. 
    - Do NOT talk about applying labels
    - Do NOT use variable names. 
    - Restrict this list to only the variables you are using in your analysis. This is likely not to be more than 4-6. 
8. Fully describe your main explanatory variable univariately using summary statistics and graphics. 
9. Fully describe your main response variable univariately using summary statistics and graphics. 

## <span style="color:blue">**Stage 2**</span>
Slide 10-11: Bivariate graphics and analysis. 

Each slide should contain the following:  

1. A fully labeled and cleaned up plot demonstrating the bivariate relationship under consideration.
2. The results of an appropriate bivariate analysis. This should be a conclusion written in english, includes a confidence interval and a p-value. You also need to state the name of the test you used. 

Refer to the [Bivariate Inference](notes.html) assignment on how to conduct and interpret these bivariate analyses.

## <span style="color:blue">**Stage 3**</span>

Slide 12-13:  Multivariate Analysis

You are trying to understand the relationship between your explanatory and response variable, in presenece of information contained in other variables. 

**Testing for moderators, and confounders**

* Moderation:
    - If you found a moderator: Remove the bivariate graph and write up from your poster and replace with explanation of moderator and graph of significant bivariate at the 3rd variable level.
    - If you did NOT find a moderator: Include a slide stating what relationships you tested for moderation and with what variable to see if it was a moderator, explaining that it was not a moderator. No graphs needed
* Confounding: 
    - If you found a confounder: on slide with bivariate relationship that was confounded put a bullet point that explains what variable confounded the relationship and put the written results that are shown in the confounding assignment on how to write results. Make sure to explain if it helped improve prediction of response variable. 
    - If you did NOT find a confounder: Include a slide stating what relationships you tested for confounds and with what variable to see if it was a confound, explaining that it was not a moderator. Make sure to explain if it helped improve prediction of response variable. 

**Building a Multivariable Model**

* If no confounders or modifiers were found, you should build a multivariable model. 
* Include any third variables that were found to be significantly associated with the outcome (but not modifiers or confounders)
* A table or a graphic of coefficients must be presented. 
    - The `coefplot()` function in the `arm` package is an excellent way of displaying the results of a multivariable model. Here is a [blog post on coefplot](https://druedin.com/2015/02/28/how-to-create-coefficient-plots-in-r-the-easy-way/), and [another one](https://www.r-bloggers.com/coefplot-new-package-for-plotting-model-coefficients/). It's pretty straightforward to create: `my.model <- lm(your model here)` then call `coefplot(my.model)`, 
    - At least one coefficient, the primary explanatory variable, must be interpreted in context of the problem. 

Slide 14. **Discussion**

* Here you will explain what your graphical and inferential results tell you about your topic.
* Discuss if your research hypothesis was supported, if it was not, why you think that might be
* Explain the overall story/trend/what you learned when you consider your univariate, bivariate & multivariate results about your topic.
* Compare your results to previous research results. Do they agree or disagree? 

Slide 15. **Implications**

* What are the practical implications of your results?
* What could others do with your findings? 
* What future research needs to be conducted?
    - This needs to be more specific than "other variables could be explored". Which variables and why? What other research articles indicate that those other variables are relevant? 


Slide 16. **References**  

* You can use smaller font to get all references on one slide.
* Use references from research plan, and any additional references gathered along the way. 
* Make sure these are correctly done in APA format.
* Proper citations for 
    - [Add Health](http://www.cpc.unc.edu/projects/addhealth/faqs/addhealth#how-do-i-cite-the-add-health-contractual-data-)
    - *R*: Type `citation()`
    - [R Studio](https://support.rstudio.com/hc/en-us/articles/206212048-Citing-RStudio)
    - [SPSS](http://www-01.ibm.com/support/docview.wss?uid=swg21476197)
    - [How to cite software in Text](http://blog.apastyle.org/apastyle/2015/01/how-to-cite-software-in-apa-style.html)
    


# Final Posters
* You will transfer all findings into a research poster, and then present your research to your classmates. 
    - We will split the class in half. When not presneting, you will be scoring the other half of the class's posters. 
* All posters must be built in Powerpoint. No exceptions.
* Use these [poster guidelines](https://norcalbiostat.netlify.com/lec/poster_guidelines/) to see templates and develop your poster.


## Draft version
* This draft is graded on how complete the poster is. You should consider this a draft that you would circulate to your colleagues for final review and comments. 
* Use the [evaluation criteria](https://norcalbiostat.netlify.com/lec/poster_guidelines/#evaluation-criteria) as a guide for what I am looking for.  
* **Submit your poster draft** to [this Dropbox folder](https://www.dropbox.com/request/7pWvRwRGM1wRqCAl3jCB). 
* **Peer Review** 
    - Download your Assigned poster to review. 
    - Write the comments directly into the poster file itself. 
    - provide at least two specific comments for each
        - something that can be improved
        - something that is good
    - Save this file with your initials at the end of the file name. 
* **Upload your revision** to [this Google folder](https://drive.google.com/drive/folders/1_CWqJt0L9QUguxWwcaNaH84ctkLTQlS7?usp=sharing). 

<button data-toggle="collapse" data-target="#draft">Show/Hide Drafts for Review</button> 

<div id="draft" class="collapse"> 
#### Poster drafts to review. 
```{r, message=FALSE, warning=FALSE}
library(stringr); library(dplyr)
library(knitr); library(kableExtra)

dta <- data.frame(filenames = paste0('PosterDraft/', list.files("PosterDraft/")))

out <- dta %>% mutate(name = gsub("PosterDraft/",  "", filenames),
                      link = sprintf("[%s](%s)",name, filenames)) %>%
               select(link)

x = kable(out, format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)
```

</div>


<br><br>

## Poster Presentations
* Upload your final poster to [this Dropbox folder](https://www.dropbox.com/request/NtC88NHRbo5oIyRcSxoD). PDF preferred. PPTX ok.
* Scoring will be done via [Google Forms](https://goo.gl/forms/QORgO0jjqNzp3T5i2). It looks exactly like the [evaluation criteria](https://norcalbiostat.netlify.com/lec/poster_guidelines/#evaluation-criteria).
    - When not presenting, you will walk around and learn about others research. Ask them questions, fill out the evaluation on your phone as you go. Printed copies will be available upon request. 
* The final grade will be determined by
    - Base score = **30%** student score + **70%** instructor score **+ bonus pts** for best in show awards **- 1** point penalty for each day late. 

<button data-toggle="collapse" data-target="#final">Show/Hide Final Versions</button>
<div id="final" class="collapse">

```{r, message=FALSE, warning=FALSE, echo=FALSE}
dta <- data.frame(filenames = paste0('FinalPoster/', list.files("FinalPoster/")))

out <- dta %>% mutate(name = gsub("FinalPoster/",  "", filenames),
                      link = sprintf("[%s](%s)",name, filenames)) %>%
               select(link)

x = kable(out, format="html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                  full_width=FALSE,  position = "left")
gsub("<thead>.*</thead>", "", x)

```

</div>

