---
title: "Schedule"
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(kableExtra);library(stringr); library(pander)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# Last Updated: `r format(Sys.time(), "%a %b %d %X")` {.tabset .tabset-fade .tabset-pills}

## Overview

<p>
Unless specified otherwise, all assignments are due at midnight on the due date listed.
</p>
```{r}
# Read in schedule
rawdat <- read_xlsx("schedule_315.xlsx", sheet='weekly_schedule')

# Set semester start date and format weeks nicely
start.date <- as.Date("2019-08-19")
wn <- which(!is.na(rawdat$wknum)) # which rows have week numbers
wkdt <- rawdat$wknum[wn]*7 + start.date # get the week dates
weekdates <- paste0("Week ", rawdat$wknum[wn], " (", format(wkdt, "%m/%d") , ")") # format the display
#link <- paste0("wk/wk", rawdat$wknum, ".html") # create link to weekly detail webpage
#week_details <- sprintf("[%s](%s)",rawdat$Week[wn], link[wn]) # put it together

# Filter rows to display on schedule
out <- rawdat[which(rawdat$Order==1.1):nrow(rawdat), ]%>% select(Topic:Assignments)

#week <- grep("midterm|final", out$Topic, ignore.case=TRUE)

# add bullets to materials
#mats <- which(!is.na(out$Materials))
#out$Materials[mats] <- paste0("<ul><li>", out$Materials[mats], "</li></ul>")
#out$Materials[mats] <- gsub("\r\n", "</li><li>", out$Materials[mats])

# add bold to due dates
out$Assignments <- gsub(" (", " (<b>", out$Assignments, fixed=TRUE)
out$Assignments <- gsub(" )", "</b>)", out$Assignments, fixed=TRUE)
out$Quiz <- gsub(" (", " (<b>", out$Quiz, fixed=TRUE)
out$Quiz <- gsub(" )", "</b>)", out$Quiz, fixed=TRUE)

wk.labs <-  "background-color: #4d6600; color: #fff;"
```

```{r, results='asis'}
out %>% 
  kable(align="lccclc", escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>% 
  pack_rows(weekdates[1], wn[1],  wn[2]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[2], wn[2],  wn[3]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[3], wn[3],  wn[4]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[4], wn[4],  wn[5]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[5], wn[5],  wn[6]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[6], wn[6],  wn[7]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[7], wn[7],  wn[8]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[8], wn[8],  wn[9]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[9], wn[9],  wn[10]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[10], wn[10],  wn[11]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[11], wn[11],  wn[12]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[12], wn[12],  wn[13]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[13], wn[13],  wn[14]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[14], wn[14],  wn[15]-1, label_row_css =wk.labs) %>%
  pack_rows(weekdates[15], wn[15],  wn[16]-1, label_row_css =wk.labs) %>%
  pack_rows(paste0("Finals Week (", weekdates[16], ")"), wn[16],  nrow(rawdat), 
            label_row_css =wk.labs) %>%
  column_spec(1, width = "35%") %>% 
  column_spec(2, width = "7%") %>%
  column_spec(3, width = "7%") %>%
  column_spec(4, width = "10%") %>% 
  column_spec(5, width = "35%")
```

## Details

Click each link to expand or contract the details for that week. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Read in schedule
raw_detail <- read_excel("schedule_315.xlsx", sheet="slo_detail")

# Function to extract week and display data
details <- function(w){
  wd <- filter(raw_detail, wk==w) %>% select(SLO, Prepare, Monday, Wednesday, Friday)  
  # strip data columns into separate lists
  SLO  <- as.list(str_split(wd$SLO, "\r\n", simplify=TRUE))
  prep <- as.list(str_split(wd$Prepare, "\r\n", simplify=TRUE))
  mon  <- as.list(str_split(wd$Monday, "\r\n", simplify=TRUE))
  wed  <- as.list(str_split(wd$Wednesday, "\r\n", simplify=TRUE))
  fri  <- as.list(str_split(wd$Friday, "\r\n", simplify=TRUE))
  
  return(list(SLO=SLO, prep=prep, mon=mon, wed=wed, fri=fri))
}

```

### <a href="#week1" data-toggle="collapse">Week 1: Getting Started with data</a>
<div id="week1" class="collapse">

#### Learning Objectives
By the end of the week, learners will be able to: 
```{r}
w1 <- details(1)
pander(w1$SLO)
```

#### How to prepare
```{r}
pander(w1$prep)
```

#### Monday overview
```{r}
pander(w1$mon)
```

#### Wednesday overview
```{r}
pander(w1$wed)
```

#### Friday overview
```{r}
pander(w1$fri)
```

</div>




### <a href="#week2" data-toggle="collapse">Week 2: Choosing a Research Project</a>
<div id="week2" class="collapse">

#### Learning Objectives
```{r}
w2 <- details(2)
pander(w2$SLO)
```

#### How to prepare
```{r}
pander(w2$prep)
```

#### Monday overview
```{r}
pander(w2$mon)
```

#### Wednesday overview
```{r}
pander(w2$wed)
```

#### Friday overview
```{r}
pander(w2$fri)
```

</div>







### <a href="#week3" data-toggle="collapse">Week 3: Working with Data</a>
<div id="week3" class="collapse">

#### Learning Objectives
```{r}
w3 <- details(3)
pander(w3$SLO)
```

#### How to prepare
```{r}
pander(w3$prep)
```

#### Monday overview
```{r}
pander(w3$mon)
```

#### Wednesday overview
```{r}
pander(w3$wed)
```

#### Friday overview
```{r}
pander(w3$fri)
```

</div>

### <a href="#week4" data-toggle="collapse">Week 4: Describing Data</a>
<div id="week4" class="collapse">

#### Learning Objectives
```{r}
w4 <- details(4)
pander(w4$SLO)
```

#### How to prepare
```{r}
pander(w4$prep)
```

#### Monday overview
```{r}
pander(w4$mon)
```

#### Wednesday overview
```{r}
pander(w4$wed)
```

#### Friday overview
```{r}
pander(w4$fri)
```

</div>


### <a href="#week5" data-toggle="collapse">Week 5: Graphing Relationships</a>
<div id="week5" class="collapse">

#### Learning Objectives
```{r}
w5 <- details(5)
pander(w5$SLO)
```

#### How to prepare
```{r}
pander(w5$prep)
```

#### Monday overview
```{r}
pander(w5$mon)
```

#### Wednesday overview
```{r}
pander(w5$wed)
```

#### Friday overview
```{r}
pander(w5$fri)
```

</div>


### <a href="#week6" data-toggle="collapse">Week 6: Writing about research, probability, midterm</a>
<div id="week6" class="collapse">

#### Learning Objectives
```{r}
w6 <- details(6)
pander(w6$SLO)
```

#### How to prepare
```{r}
pander(w6$prep)
```

#### Monday overview
```{r}
pander(w6$mon)
```

#### Wednesday overview
```{r}
pander(w6$wed)
```

#### Friday overview
```{r}
pander(w6$fri)
```

</div>


### <a href="#week7" data-toggle="collapse">Week 7: Estimating Parameters with uncertainty</a>
<div id="week7" class="collapse">

#### Learning Objectives
```{r}
w7 <- details(7)
pander(w7$SLO)
```

#### How to prepare
```{r}
pander(w7$prep)
```

#### Monday overview
```{r}
pander(w7$mon)
```

#### Wednesday overview
```{r}
pander(w7$wed)
```

#### Friday overview
```{r}
pander(w7$fri)
```

</div>


### <a href="#week8" data-toggle="collapse">Week 8: Inferential Analysis</a>
<div id="week8" class="collapse">

#### Learning Objectives
```{r}
w8 <- details(8)
pander(w8$SLO)
```

#### How to prepare
```{r}
pander(w8$prep)
```

#### Monday overview
```{r}
pander(w8$mon)
```

#### Wednesday overview
```{r}
pander(w8$wed)
```

#### Friday overview
```{r}
pander(w8$fri)
```

</div>




### <a href="#week9" data-toggle="collapse">Week 9: Bivariate Inference</a>
<div id="week9" class="collapse">

#### Learning Objectives
```{r}
w9 <- details(9)
pander(w9$SLO)
```

#### How to prepare
```{r}
pander(w9$prep)
```

#### Monday overview
```{r}
pander(w9$mon)
```

#### Wednesday overview
```{r}
pander(w9$wed)
```

#### Friday overview
```{r}
pander(w9$fri)
```

</div>




### <a href="#week10" data-toggle="collapse">Week 10: Regression Modeling</a>
<div id="week10" class="collapse">

#### Learning Objectives
```{r}
w10 <- details(10)
pander(w10$SLO)
```

#### How to prepare
```{r}
pander(w10$prep)
```

#### Monday overview
```{r}
pander(w10$mon)
```

#### Wednesday overview
```{r}
pander(w10$wed)
```

#### Friday overview
```{r}
pander(w10$fri)
```

</div>




### <a href="#week11" data-toggle="collapse">Week 11: Considering additional measures</a>
<div id="week11" class="collapse">

#### Learning Objectives
```{r}
w11 <- details(11)
pander(w11$SLO)
```

#### How to prepare
```{r}
pander(w11$prep)
```

#### Monday overview
```{r}
pander(w11$mon)
```

#### Wednesday overview
```{r}
pander(w11$wed)
```

#### Friday overview
```{r}
pander(w11$fri)
```

</div>




### <a href="#week12" data-toggle="collapse">Week 12: Multivariable Regression analysis</a>
<div id="week12" class="collapse">

#### Learning Objectives
```{r}
w12 <- details(12)
pander(w12$SLO)
```

#### How to prepare
```{r}
pander(w12$prep)
```

#### Monday overview
```{r}
pander(w12$mon)
```

#### Wednesday overview
```{r}
pander(w12$wed)
```

#### Friday overview
```{r}
pander(w12$fri)
```

</div>




### <a href="#week13" data-toggle="collapse">Week 13: Logistic Regression</a>
<div id="week13" class="collapse">

#### Learning Objectives
```{r}
w13 <- details(13)
pander(w13$SLO)
```

#### How to prepare
```{r}
pander(w13$prep)
```

#### Monday overview
```{r}
pander(w13$mon)
```

#### Wednesday overview
```{r}
pander(w13$wed)
```

#### Friday overview
```{r}
pander(w13$fri)
```

</div>




### <a href="#week14" data-toggle="collapse">Week 14: Model building strategies</a>
<div id="week14" class="collapse">

#### Learning Objectives
```{r}
w14 <- details(14)
pander(w14$SLO)
```

#### How to prepare
```{r}
pander(w14$prep)
```

#### Monday overview
```{r}
pander(w14$mon)
```

#### Wednesday overview
```{r}
pander(w14$wed)
```

#### Friday overview
```{r}
pander(w14$fri)
```

</div>




### <a href="#week15" data-toggle="collapse">Week 15: Disseminating Research</a>
<div id="week15" class="collapse">

#### Learning Objectives
```{r}
w15 <- details(15)
pander(w15$SLO)
```

#### How to prepare
```{r}
pander(w15$prep)
```

#### Monday overview
```{r}
pander(w15$mon)
```

#### Wednesday overview
```{r}
pander(w15$wed)
```

#### Friday overview
```{r}
pander(w15$fri)
```

</div>





## Calendar

For those of you that like the calendar view of your schedule. Due to schedule adjustments during
the semester these dates may not match exactly with the schedule. In those cases please bring any 
descrepencies to my attention via Slack. 

<iframe src="https://calendar.google.com/calendar/embed?src=mail.csuchico.edu_16sj77sfemp9kqgis2g89j91e0%40group.calendar.google.com&ctz=America%2FLos_Angeles" style="border: 0" width="800" height="600" frameborder="0" scrolling="no"></iframe>

