---
title: "Math 315"
output: 
  html_document: 
    highlight: default
    css: style.css
---
```{r, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse);library(readxl); library(kableExtra);library(stringr); library(pander)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# _Last Updated: `r format(Sys.time(), "%a %b %d %X")`_ {.tabset .tabset-fade .tabset-pills}

## Overview

<p>
Unless specified otherwise, all assignments are due at midnight on the due date listed.  

Lecture/practice notes will be released *after* the topic is completed in class. This gives you time to fill out the course packet out of your own brain first (recall), then you can review these notes to catch something you missed. 

<br>

Some videos linked were created by Dr. Gray in fall for her section of 350. Most examples she works through should be identical to the ones in the course packet, but there likely will be deviations. 

<a href="https://forms.gle/D86w12njtjgX7yBN7"><button type="button">Anonymous Feedback Form</button> </a>

</p>

```{r}
# Read in schedule
rawdat <- read_xlsx("_math350_schedule.xlsx", sheet='weekly_schedule') 

# content rows
content  <- rawdat %>% filter(is.na(tnum))

# which rows have topic numbers 
tn <- rawdat %>% filter(!is.na(tnum)) %>% 
        select(tnum, Topic) %>%
        mutate(start=0, end=0)

for(t in 1:max(tn$tnum)){
  tn$start[t] <- min(which(floor(content$Order)==t))
  tn$end[t]   <- max(which(floor(content$Order)==t))
}

out <- content %>%
  # wrangle hw links
  separate(col=Do, into=c("hw.name", "hw.link", "hw.due"), sep="-| ") %>%
  mutate(Date = format(Date,"%m/%d"),
         hw.due = gsub("(", "<b> \r\n Due (", hw.due, fixed=TRUE), 
         hw.due = gsub(")", ")</b>" , hw.due, fixed=TRUE),
         hw.sol = ifelse(!is.na(sol), sol, ""), 
         Do = ifelse(!is.na(hw.name), 
                     paste0(sprintf("[%s](%s)", hw.name, hw.link), 
                            "<br>", hw.due, "<br>", hw.sol), 
                     NA), 
         Notes = ifelse(!is.na(Notes),Notes, NA)) %>%
  select(Date, Topic, Notes, Read, Watch, Practice = Do, Assess=quiz) 


# highlight rows
wk.labs <-  "background-color: #bb9457; color: #fff;"
hlt.wks <-  "background-color: #6f1d1b; color: #fff;"
```

```{r, results='asis'}
out %>% 
  kable(align="cllllcc", escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered")) %>% 
  pack_rows(tn$Topic[1], tn$start[1],   tn$end[1], label_row_css =wk.labs) %>% 
  pack_rows(tn$Topic[2], tn$start[2],   tn$end[2], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[3], tn$start[3],   tn$end[3], label_row_css =hlt.wks) %>%
  pack_rows(tn$Topic[4], tn$start[4],   tn$end[4], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[5], tn$start[5],   tn$end[5], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[6], tn$start[6],   tn$end[6], label_row_css =hlt.wks) %>%
  pack_rows(tn$Topic[7], tn$start[7],   tn$end[7], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[8], tn$start[8],   tn$end[8], label_row_css =wk.labs) %>%
  pack_rows(tn$Topic[9], tn$start[9],   tn$end[9], label_row_css =hlt.wks) %>%
  column_spec(1, width = "5%") %>% 
  column_spec(2, width = "22%") %>%
  column_spec(3, width = "15%") %>%
  column_spec(4, width = "3%") %>% 
  column_spec(5, width = "25%") %>%
  column_spec(6, width = "15%") %>%
  column_spec(7, width = "15%")
```



## Weekly Details


